### 2020-03-16 writeup/setup.tex
wip

@@

\begin{proposition}\label{prop_monotone}
  When there is no model shift, adding the source task data always reduces the estimation error, i.e.
	\[ e(\hat{\beta}_{s,t}) \le e(\hat{\beta}_t). \]
\end{proposition}

@@

\subsection{Objectives}

We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on two objectives.
\begin{itemize}
	\item Estimation error for the target model $\beta_t$: we consider their distance
		\[ \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
	\item Test error for the target task:
		\[ \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}}. \]
\end{itemize}
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

>>>>

\paragraph{Objectives.}
We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on two objectives.
\begin{itemize}
	\item Estimation error for the target model $\beta_t$: we consider their distance
		\[ e(\hat{\beta}) \define \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
	\item Test error for the target task:
		\begin{align*}
			te(\hat{\beta}) &\define \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}} \\
			&= \exarg{\varepsilon_i, \forall 1\le i\le k}{(\hat{\beta} - \beta_t)^{\top}\Sigma_k(\hat{\beta} - \beta_t)}.
		\end{align*}
\end{itemize}
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

@@

\begin{proposition}\label{prop_monotone}
	Suppose that $n > p$.
  When there is no model shift, adding the source task data always reduces the estimation error, i.e.
	\[ e(\hat{\beta}_{s,t}) \le e(\hat{\beta}_t). \]
\end{proposition}

@@
